\section{Motivation}

\begin{frame}{Motivation}

  \begin{itemize}
    \item Exploration and Exploitation
      \begin{itemize}
        \item Exploration: the ability to have an overview to the search
          space.
        \item Exploitation: the ability to generate high resolution
          solutions.
        \item CMA-ES preforms outstandingly on exploitation.
      \end{itemize}
      \vspace*{14pt}
    \item Easily trapped into local optima due to the ability of
      exploitation.
      \begin{itemize}
        \item Lack of diversity
        \item Typical evolutionary algorithms adopt a larger initial
          population size.
        \item CMA-ES benefits nothing from a larger initial population
          size.
      \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{Hypothesis}

  \begin{itemize}
    \item Increasing diversity by maintaining multiple groups.
      \begin{itemize}
        \item kind of discretization.
        \item How to define the number of groups?
        \item What is the criteria for individuals to form a group?
      \end{itemize}
      \vspace*{14pt}
    \item There is implicit information hidden between groups.
      \begin{itemize}
        \item How to extract the information?
        \item How to benefit from the information and obtain
          better solutions?
          \begin{itemize}
            \item Inspired by discretization, we aim to find a more
              promising region.
          \end{itemize}
      \end{itemize}
      \vspace*{14pt}
    \item 2-layer CMA-ES is introduced
      \begin{itemize}
        \item Inner layer for exploitation
        \item Outer layer for exploration
      \end{itemize}
  \end{itemize}

\end{frame}
